The Revisited Hidden Weight Bit Function

### 2025-11-28 paper.tex
M

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{microtype}

@@

\author{%
    Pierrick Méaux\inst{1}\orcidID{0000-0001-5733-4341} \and
    Tim Seuré\inst{1}\orcidID{0000-0003-4200-7553} \and %Corresponding author
    Deng Tang\inst{2}\orcidID{0000-0002-8373-9200}
}
\authorrunning{P. Méaux \etal}

\institute{%
    University of Luxembourg, Luxembourg\\
    \email{pierrick.meaux@uni.lu, tim.seure@uni.lu} 
    \and
    Shanghai Jiao Tong University, Shanghai, China\\
    \email{dengtang@sjtu.edu.cn}
}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{marvosym}
\usepackage{microtype}
\usepackage{orcidlink}

@@

\author{%
    Pierrick Méaux\inst{1}\orcidlink{0000-0001-5733-4341} \and
    Tim Seuré\textsuperscript{(\Letter)}\inst{1}\orcidlink{0000-0003-4200-7553} \and
    Deng Tang\inst{2}\orcidlink{0000-0002-8373-9200}
}
\authorrunning{P. Méaux \etal}

\institute{%
    University of Luxembourg, Esch-sur-Alzette, Luxembourg\\
    \email{pierrick.meaux@uni.lu, tim.seure@uni.lu} 
    \and
    Shanghai Jiao Tong University, Shanghai, China\\
    \email{dengtang@sjtu.edu.cn}
}
